Supplementary appendix

### 2018-07-01 paper2_APPENDIX.Rmd
Add files via upload

In the tables below, I present additional robust analyses for the effect of symbols on trust in policy and its interaction with the information of the policy plans. In **Table A3**, I replicate table 1 of the main paper on the full, unfiltered sample, excluding subjects who are under the age of 18 (n_subjects = `r SVIVA2_comb_robust_1 %>%distinct(IP) %>% nrow()`). In **Table A4**, I add a set of control variables. In **Table A5** and **Table A6**, I exclude those subjects who did not recognize the real symbols which were included in the communications. Table A5 excludes those who did not recognize the campaign images (n_subjects = `r SVIVA2_comb_robust_3 %>%distinct(IP) %>% nrow()`) and Table A6 excludes those who did not recognize EPM's logo (n_subjects = `r SVIVA2_comb_robust_4 %>%distinct(IP) %>% nrow()`). Finally, in **Table A7**, I add interactions with the policy plan, to examine whether the effect of the symbols were significanly different for these two policies. All these analyses are random-effect GLS regressions clustered at the subject level, similarly to the main models presented in the paper.

In all these supplementary analyses, the main effect of the real symbols on trust in policy is significant, and the interaction bewteen the real symbols and the weak inforamtion remains positive and significant.

@@

stargazer(mod_1.1,mod_1.2,mod_1.3,
          type="html",style = "apsr",
          dep.var.labels=c("Trust in policy (combined)"),
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak policy (0=strong policy)",
                             "Weak policy x Real symbols",
                             "Weak policy x Fake symbols"),
          initial.zero = FALSE,
          omit.stat = c("aic","bic"),
          notes = "*Notes*: Table entries are non-standardized random-effect GLS regression coefficients, clustered at the subject level. Standard errors are in parentheses. The reference category for the symbols manipulation conditions is the control no-symbols.",
          notes.append = FALSE)
```

@@

stargazer(mod_1.1,mod_1.2,mod_1.3,
          type="html",style = "apsr",
          dep.var.labels=c("Trust in policy (combined)"),
          initial.zero = FALSE,
          omit.stat = c("aic","bic"),
          order = c(1,2,3,10,11,4,5,6,7,8,9),
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak policy (0=strong policy)",
                             "Weak policy x Real symbols",
                             "Weak policy x Fake symbols",
                             "Gender (1=Woman)",
                             "Ideology",
                             "Trust in government ministries",
                             "Income",
                             "Education",
                             "Residence in Haifa-Bay area"),
          notes = "*Notes*: Table entries are non-standardized random-effect GLS regression coefficients, clustered at the subject level. Standard errors are in parentheses. The reference category for the symbols manipulation conditions is the control no-symbols.",
          notes.append = FALSE)
```

@@

stargazer(mod_1.1,mod_1.2,mod_1.3,
          type="html",style = "apsr",
          dep.var.labels=c("Trust in policy (combined)"),
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak policy (0=strong policy)",
                             "Weak policy x Real symbols",
                             "Weak policy x Fake symbols"),
          initial.zero = FALSE,
          omit.stat = c("aic","bic"),
          notes = "*Notes*: Table entries are non-standardized coefficients. Standard errors are in parentheses. The reference category for the symbols manipulation conditions is the control no-symbols.",
          notes.append = FALSE)
```

@@

stargazer(mod_1.1,mod_1.2,mod_1.3,mod_1.4,
          type="html",style = "apsr",
          dep.var.labels=c("Trust in policy (combined)"),
          order = c(2,3,4,8,9,1,5,6,7,10,11),
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak policy (0=strong policy)",
                             "Weak policy x Real symbols",
                             "Weak policy x Fake symbols",
                             "Policy (1=recycling)",
                             "Policy x Real symbols",
                             "Policy x Fake symbols",
                             "Policy x Weak policy",
                             "Policy x Weak policy x Real symbols",
                             "Policy x Weak policy x Fake symbols"),
          initial.zero = FALSE,
          omit.stat = c("aic","bic"),
          notes = "*Notes*: Table entries are non-standardized random-effect GLS regression coefficients, clustered at the subject level. Standard errors are in parentheses. The reference category for the symbols manipulation conditions is the control no-symbols.",
          notes.append = FALSE)
```

@@

**Greetings, We are researchers from the Department of Political Science at the Hebrew University. The short questionnaire below is part of an academic study designed to teach us about the attitudes of Israeli citizens regarding environmental policy. Therefore, it is important for us that you answer the questionnaire seriously and honestly. The questionnaire filling time is about 5-10 minutes.**

@@

**Now, we would like to ask you a few general questions about your area of occupation**

**In which sector are you currently employed:?**

@@

**What, in your opinion, might attract people to choose your occupation?? _________________________________________**

@@

**HWhat is your age?**
10----20----30----40----50----60----70----80

@@

**In which residential area do you currently live?**
1. North

@@

You can review the original policies of the Environmental Protection Ministry regarding the policy issues which were presented at the website of government work plans: plans.gov.il and at the Ministry's website: sviva.gov.il.

>>>>

In the tables below, I report the results of additional robust analyses testing the effect of the manipulation of symbols on trust in policy and its interaction with the manipulation of information in policy plans. **Table A3** replicates table 1 of from the paper, while adding those subjects who were filttered, except for those who are under the age of 18 (n_subjects = `r SVIVA2_comb_robust_1 %>%distinct(IP) %>% nrow()`). In **Table A4**, replicate Table 1 while adding a set of control variables. In **Table A5** and **Table A6**, I exclude those subjects who did not recognize the real symbols which were included in the communications. Table A5 excludes those who did not recognize the campaign images (n_subjects = `r SVIVA2_comb_robust_3 %>%distinct(IP) %>% nrow()`) and Table A6 excludes those who did not recognize EPM's logo (n_subjects = `r SVIVA2_comb_robust_4 %>%distinct(IP) %>% nrow()`). Finally, in **Table A7**, I examine whether the effect of the symbols were significanly different for the two policies, by adding the interactions with the policy plan. All these analyses are random-effect GLS regressions clustered at the subject level, similarly to the main models presented in the paper. In all these supplementary analyses, the effects of the real symbols and their interaction with information are consistent with the main models presented in the paper. The main effect of the real symbols on trust in policy is significant, and the interaction bewteen the real symbols and the weak inforamtion remains positive and significant.

@@

stargazer(mod_1.1,mod_1.2,mod_1.3,
          type="html",style = "apsr",
          dep.var.labels=c("Trust in policy"),
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak policy (0=strong policy)",
                             "Weak policy x Real symbols",
                             "Weak policy x Fake symbols"),
          initial.zero = FALSE,
          omit.stat = c("aic","bic"),
          notes = "*Notes*: Table entries are non-standardized random-effect GLS regression coefficients, clustered at the subject level. Standard errors are in parentheses. The reference category for the symbols manipulation conditions is the control no-symbols.",
          notes.append = FALSE)
```

@@

stargazer(mod_1.1,mod_1.2,mod_1.3,
          type="html",style = "apsr",
          dep.var.labels=c("Trust in policy"),
          initial.zero = FALSE,
          omit.stat = c("aic","bic"),
          order = c(1,2,3,10,11,4,5,6,7,8,9),
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak policy (0=strong policy)",
                             "Weak policy x Real symbols",
                             "Weak policy x Fake symbols",
                             "Gender (1=Woman)",
                             "Ideology",
                             "Trust in government ministries",
                             "Income",
                             "Education",
                             "Residence in Haifa-Bay area"),
          notes = "*Notes*: Table entries are non-standardized random-effect GLS regression coefficients, clustered at the subject level. Standard errors are in parentheses. The reference category for the symbols manipulation conditions is the control no-symbols.",
          notes.append = FALSE)
```

@@

stargazer(mod_1.1,mod_1.2,mod_1.3,
          type="html",style = "apsr",
          dep.var.labels=c("Trust in policy"),
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak policy (0=strong policy)",
                             "Weak policy x Real symbols",
                             "Weak policy x Fake symbols"),
          initial.zero = FALSE,
          omit.stat = c("aic","bic"),
          notes = "*Notes*: Table entries are non-standardized coefficients. Standard errors are in parentheses. The reference category for the symbols manipulation conditions is the control no-symbols.",
          notes.append = FALSE)
```

@@

stargazer(mod_1.1,mod_1.2,mod_1.3,mod_1.4,
          type="html",style = "apsr",
          dep.var.labels=c("Trust in policy"),
          order = c(2,3,4,8,9,1,5,6,7,10,11),
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak policy (0=strong policy)",
                             "Weak policy x Real symbols",
                             "Weak policy x Fake symbols",
                             "Policy (1=recycling)",
                             "Policy x Real symbols",
                             "Policy x Fake symbols",
                             "Policy x Weak policy",
                             "Policy x Weak policy x Real symbols",
                             "Policy x Weak policy x Fake symbols"),
          initial.zero = FALSE,
          omit.stat = c("aic","bic"),
          notes = "*Notes*: Table entries are non-standardized random-effect GLS regression coefficients, clustered at the subject level. Standard errors are in parentheses. The reference category for the symbols manipulation conditions is the control no-symbols.",
          notes.append = FALSE)
```

@@

**Greetings,**

**We are researchers from the Department of Political Science at the Hebrew University. The short questionnaire below is part of an academic study designed to teach us about the attitudes of Israeli citizens regarding environmental policy. Therefore, it is important for us that you answer the questionnaire seriously and honestly. The questionnaire filling time is about 5-10 minutes.**

@@

**Now, we would like to ask you a few general questions about your area of occupation.**

**In which sector are you currently employed?**

@@

**What, in your opinion, might attract people to choose your occupation? _________________________________________**

@@

**What is your age?**

10----20----30----40----50----60----70----80

@@

@@

**You may review the original policies of the Environmental Protection Ministry regarding the policy issues which were presented at the website of government work plans: plans.gov.il and at the Ministry's website: sviva.gov.il.**
